---
title: "LDH Cytotoxicity Assay Report"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    theme: yeti
params:
  results: NULL
---

```{r setup, include=FALSE}
# This chunk sets up the report environment
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(ggplot2)
library(knitr)
library(DT)
library(dplyr)
library(stringr)
```

# Summary of Findings

```{r summary_chunk}
# This chunk calculates the key findings to display them upfront.
df <- params$results$pairwise_df
control <- params$results$control_group_name

# Add a significance column if it doesn't exist (e.g., from Kruskal-Wallis)
if (!"significance" %in% names(df)) {
  df <- df %>% mutate(significance = ifelse(p.adjusted <= 0.05, "Yes", "No"))
}

significant_comparisons <- df %>%
  filter(str_detect(comparison, fixed(control)) & significance == "Yes")

num_significant <- nrow(significant_comparisons)
total_comparisons <- sum(str_detect(df$comparison, fixed(control)))

# Generate the summary sentence
summary_sentence <- sprintf(
  "The analysis was performed using a **%s**. Out of **%d** treatments compared against the control group ('%s'), **%d** showed a statistically significant difference in cytotoxicity.",
  params$results$test_name,
  total_comparisons,
  control,
  num_significant
)
```

`r summary_sentence`

-----

# Cytotoxicity Plot

The plot below visualizes the cytotoxicity levels for each treatment group. Significance brackets indicate comparisons against the selected control group, **`r params$results$control_group_name`**.

```{r plot, fig.width=10, fig.height=6}
print(params$results$final_plot)
```

-----

# Detailed Analysis {.tabset}

This section provides the detailed statistical outputs, including the overall test results, pairwise comparisons, and assumption checks.

### Statistical Summary

The choice of statistical test was determined by the user's selection and the results of diagnostic assumption checks.

**Test Performed:** `r params$results$test_name`

**Overall (Omnibus) Test Result:** `r params$results$omnibus_text`

This initial test determines if there is any significant difference *somewhere* among all the groups analyzed.

### Pairwise Comparisons

If the omnibus test was significant, a post-hoc test was run to compare every pair of groups. The table below shows the adjusted p-values for these comparisons. A p-value ≤ 0.05 is typically considered statistically significant.

```{r table}
datatable(
  params$results$pairwise_df,
  caption = "Pairwise comparison results.",
  options = list(pageLength = 10, searching = TRUE),
  rownames = FALSE
)
```

### Assumption Checks

Parametric tests like ANOVA are most reliable when certain assumptions about the data's distribution are met.

**1. Normality of Residuals (Shapiro-Wilk Test)**

  * This test checks if the model's errors are normally distributed.
  * The p-value was **`r round(params$results$shapiro_p, 4)`**. The assumption is met if the p-value is \> 0.05.

**2. Homogeneity of Variances (Levene's Test)**

  * This test checks if the variance (or spread) of the data is equal across all groups.
  * The p-value was **`r round(params$results$levene_p, 4)`**. The assumption is met if the p-value is \> 0.05.

<!-- end list -->

```{r qqplot, fig.width=6, fig.height=5}
print(params$results$qq_plot)
```

The Q-Q plot above provides a visual check for the normality assumption.
